### 2013-07-05 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
reworking titan scaling data and adding addtional runs for averaging

In the next set of scaling studies, we will explore how adding overlap
to the subdomains in the problem affects runtimes and parallel
performance as compared to the case with pure domain decomposition. To
do this, we utilize the set of analytic relations developed in
\S~\ref{sec:analytic_framework} to design these numerical
experiments. For the neutron diffusion problem used in these scaling
studies, the linear operator had a spectral radius of 0.787 and a
weight cutoff of \sn{1}{-2}. Using Eq~(\ref{eq:analytic_k}) gives an
expected random walk length of 19.22 transitions for any given history
in the problem. Using the mean-chord approximation given by
Eq~(\ref{eq:mean_chord_domain_leakage}), we then expect approximately
5.3\% of the histories born in a particular domain to leak out after
the first transport stage. By adding overlap, we aim to reduce this
fraction of communicated histories and therefore boost the parallel
performance of the algorithm. To determine the amount of overlap to
test for the scaling studies, we use a variation of
Eq~(\ref{eq:step_k_length}) to determine how many discrete states a
history will move on average from its birth site. We modify
Eq~(\ref{eq:step_k_length}) to only account for discrete movements:
\begin{equation}
  \sqrt{\bar{n^2_k}} = n_s \sqrt{k}\:,
  \label{eq:discrete_distance}
\end{equation}
where $\sqrt{\bar{n^2_k}}$ is now the root-mean-squared number of
discrete states a history will move from its birth site. For our
diffusion problem used in these scaling studies, we compute a value of
2.63 states per history for any of the dimensions of the system. For
this diffusion problem, this means that we can expect to end up on
average 2.63 states in both the $i$ and $j$ dimensions away from the
starting state. Therefore, we will use the overlap generation
algorithm outlined in \S~\ref{subsec:msod_generation} such that we
parameterically grow the local domain using 1, 2, 3, and 5 levels to
measure how scalability is affected when this root-mean-squared number
of states is considered. For example, using 3 levels of overlap should
keep over 50\% of the histories that would be communicated in the pure
domain decomposition case on-process as this is greater than the
root-mean-squared number of states we would expect a history to
travel.

For the performance metrics, we may use the same weak and strong
scaling efficiency metrics that we used for the pure domain
decomposition case. As we are comparing to the case without overlap
and are looking to boost performance relative to the case without
overlap, for both weak and strong scaling calculations we will use the
16-core case without overlap as the reference computation for all
efficiency measures reported. Doing this, permits an analysis of well
the computational resources are utilized with the overlap relative to
the case without.

>>>>

In the next set of scaling studies, we will explore how adding overlap
to the subdomains in the problem affects runtimes and parallel
performance as compared to the case with pure domain decomposition. To
do this, we utilize the set of analytic relations developed in
\S~\ref{sec:analytic_framework} to design these numerical
experiments. For the neutron diffusion problem used in these scaling
studies, the linear operator had a spectral radius of 0.787 and a
weight cutoff of \sn{1}{-2}. Using Eq~(\ref{eq:analytic_k}) gives an
expected random walk length of 19.22 transitions for any given history
in the problem. Using the mean-chord approximation given by
Eq~(\ref{eq:mean_chord_domain_leakage}), we then expect approximately
5.3\% of the histories born in a particular domain to leak out after
the first transport stage. By adding overlap, we aim to reduce this
fraction of communicated histories and therefore boost the parallel
performance of the algorithm. To determine the amount of overlap to
test for the scaling studies, we use a variation of
Eq~(\ref{eq:step_k_length}) to determine how many discrete states a
history will move on average from its birth site. We modify
Eq~(\ref{eq:step_k_length}) to only account for discrete movements:
\begin{equation}
  \sqrt{\bar{n^2_k}} = n_s \sqrt{k}\:,
  \label{eq:discrete_distance}
\end{equation}
where $\sqrt{\bar{n^2_k}}$ is now the root-mean-squared number of
discrete states a history will move from its birth site. For our
diffusion problem used in these scaling studies, we compute a value of
2.63 states per history for any of the dimensions of the system. This
means that we can expect to end up on average 2.63 states in both the
$i$ and $j$ dimensions away from the starting state. Therefore, we
will use the overlap generation algorithm outlined in
\S~\ref{subsec:msod_generation} such that we parameterically grow the
local domain using 1, 2, 3, and 5 levels to measure how scalability is
affected when this root-mean-squared number of states is
considered. For example, using 3 levels of overlap should keep over
50\% of the histories that would be communicated in the pure domain
decomposition case on-process as this is greater than the
root-mean-squared number of states we would expect a history to
travel.

For the performance metrics, we may use the same weak and strong
scaling efficiency metrics that we used for the pure domain
decomposition case. As we are comparing to the case without overlap
and are looking to boost performance relative to the case without
overlap, for both weak and strong scaling calculations we will use the
16-core case without overlap as the reference computation for all
efficiency measures reported.
